### 2015-11-05 CVPR16/Source/abstract.tex
Update Intro

\begin{abstract}
This paper studies the problem of segmenting tracked feature points of multiple objects in a video sequence. We consider scenes that contain both dynamic and static objects, which usually appear in the context of autonomous driving (e.g., moving and parked cars), and occlusions among objects. We propose a novel continuous model for representing objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions. Detailed experiments on the KITTI dataset show the superiority of the propose method over the baseline method which simply uses detection bounding boxes for resolving occlusions and other state-of-the-art motion segmentation methods which cannot cope well with static objects. As a notable application, we show how our continuous occlusion model benefits the task of 3D localization in autonomous driving.  
\end{abstract}

>>>>

\begin{abstract}
This paper studies the problem of segmenting tracked feature points of multiple objects in a video sequence. We consider scenes that contain both dynamic and static objects, which usually appear in the context of autonomous driving (e.g., moving and parked cars), and occlusions among objects. We propose a novel continuous model for representing objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions. Detailed experiments on the KITTI dataset show the superiority of the proposed method over the baseline method which simply uses detection bounding boxes for resolving occlusions and other state-of-the-art motion segmentation methods which cannot cope well with static objects. As a notable application, we show how our continuous occlusion model benefits the task of 3D localization in autonomous driving.  
\end{abstract}

### 2015-11-05 CVPR16/Source/intro.tex
Update Intro

In this work, we first propose to represent objects as 3D ellipsoids. Motivated by image formulation theory in computer graphics, we then develop novel \emph{transmission} and \emph{reflection} models, which can explicitly reason about object occlusions. Leveraging on the success of object detection and tracking algorithms, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are only computed within object tracklets, which often contain both dynamic and static point tracks. As we will show later, the proposed method outperforms the baseline method which merely uses detection bounding boxes for resolving occlusions. Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art methods for motion segmentation.

>>>>

In this work, we first propose to model objects as 3D ellipsoids. Motivated by image formulation theory in computer graphics, we then develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities, which can explicitly explain image observations and reason about object occlusions. Leveraging on the success of object detection and tracking algorithms, we assume that detection bounding boxes and object tracklets are provided, thus we concentrate on segmenting point tracks that are computed only within object tracklets. As we will show in the experiments, the proposed continuous occlusion modelling method outperforms the baseline method which merely uses bounding boxes for resolving occlusions. Furthermore, our method is not based on object motions and hence does not suffer from static objects as other state-of-the-art methods for motion segmentation.

As an important contribution, we examine the applicability of the proposed model for 3D localization in autonomous driving. In contrast to the bounding box baseline method, which uses hard assignments of point tracks to objects (i.e., {0,1} probabilities), our continuous occlusion modelling method employs soft assignments (i.e., [0,1] probabilities). Consequently, it offers a unified continuous occlusion modelling for both point track and bounding box energies, which allows the use of effective optimization tools. As we will show later, the proposed model benefits the task of 3D localization in autonomous driving in terms of lower translation and dimension errors.

The rest of the paper is organized as follows: Section~\ref{sec:related} discusses related work. Section~\ref{sec:setup} describes our continuous occlusion model for road scene understanding. Section~\ref{sec:experiments} presents experimental results for point-to-object association and 3D localization. Finally, we conclude in Section~\ref{}.
